\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Bibliography}

\bibitem{fixer} Foreign exchange rates and currency conversion JSON API, URL \url{http://fixer.io/}, last visited Dec. 13, 2015
\bibitem{tomcat} Apache Tomcat - Welcome!, URL \url{http://tomcat.apache.org/}, last visit Dec. 13, 2015.
\bibitem{postgresql} PostgreSQL: The world's most advanced open source database, URL \url{http://www.postgresql.org/}, last visit Dec. 13, 2015.
\bibitem{ifi} UZH - Department for Informatics, URL \url{http://www.ifi.uzh.ch/}, last visit Dec. 3, 2015.
\bibitem{ddd} An Introduction to Domain Driven Design, URL \url{http://www.methodsandtools.com/archive/archive.php?id=97}, last visited Dec. 6, 2015
\bibitem{angular-devguide} AngularJS: Developer Guide, \newline URL \url{https://docs.angularjs.org/guide/concepts#model}, last visited Dec. 14, 2015
\bibitem{hibernate} Hibernate. Everything data. - Hibernate, URL \url{http://hibernate.org/}, last visit Nov. 18, 2015.
\bibitem{spring} Spring, URL \url{https://spring.io/}, last visit Nov. 18, 2015.
\bibitem{maven} Maven – Welcome to Apache Maven, URL \url{https://maven.apache.org/}, last visit Nov. 18, 2015.
\bibitem{dao} Core J2EE Patterns - Data Access Object, \newline URL \url{http://www.oracle.com/technetwork/java/} \newline \url{dataaccessobject-138824.html}, last visit Dec. 5, 2015
\bibitem{mockito} mockito.org, URL \url{http://mockito.org/}, last visit Nov. 18, 2015.
\bibitem{apache-fop} Apache(tm) FOP - a print formatter driven by XSL formatting objects (XSL-FO) and an output independent formatter., URL \url{https://xmlgraphics.apache.org/fop/}, last visit Dec. 12, 2015.
\bibitem{pdfsign} Communication-Systems-Group/pdfsign.js, \newline URL \url{https://github.com/Communication-Systems-Group/pdfsign.js}, last visit Jan. 21, 2016.
\bibitem{swagger} Swagger | The World's Most Popular Framework for APIs, URL \url{http://swagger.io/}, last visit Nov. 18, 2015.
\bibitem{angular} AngularJS Documentation for introduction, URL \url{https://docs.angularjs.org/guide/introduction}, last visit Nov. 18, 2015.
\bibitem{bootstrap} BootstrapDocs - Twitter Bootstrap Documentation Archive,\newline URL \url{http://bootstrapdocs.com/v3.3.5/docs/}, last visit Nov. 18, 2015.
\bibitem{bower} Bower, URL \url{http://bower.io/}, last visit Nov. 18, 2015.
\bibitem{grunt} Grunt: The JavaScript Task Runner, URL \url{http://gruntjs.com/}, last visit Nov. 18, 2015.
\bibitem{webcrypto} WebCrypto Key Discovery, \newline URL \url{http://www.w3.org/TR/webcrypto-key-discovery/}, last visit Dec. 12, 2015.
\bibitem{node} Node.js, URL \url{https://nodejs.org/en/}, last visit Nov. 18, 2015.
\bibitem{arx-signature} Learn about Digital Signatures and Electronic Signatures, URL \url{http://www.arx.com/learn/about-digital-signature/digital-signature-faq/}, last visit Dec. 5, 2015
\bibitem{ecb} European Central Bank, URL
\url{http://www.ecb.europa.eu/stats/exchange/eurofxref/html/index.en.html}, last visit Jan. 23, 2016

\bibitem{mla} Multilayered Architecture, URL
\url{http://www.javacodegeeks.com/2013/05/multilayered-architecture-1-introduction.html}, last visit Jan. 23, 2016

\bibitem{soc} Separation of Concerns, URL
\url{http://deviq.com/separation-of-concerns}, last visit Jan. 23, 2016

\bibitem{spring} The Spring Framework, URL
\url{http://www.spring.org}, last visit Jan. 23, 2016




\end{thebibliography}
